---
title: "SlateX"
author: "Jonathan Regenstein"
date: "`r Sys.Date()`"
output:
  ioslides_presentation: default
  slidy_presentation: default
subtitle: A Subscription Platform for R and Python Creators
---



```{r setup, include = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = NA, fig.height = 4)
options(htmltools.dir.version = FALSE)

library(tidyverse)
library(tidyquant)

```

<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<script>
  $(document).ready(function() {
    $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

    $('footnote').each(function(index) {
      var text  = $(this).html();
      var fnNum = (index+1).toString().sup();
      $(this).html(text + fnNum);

      var footnote   = fnNum + ': ' + $(this).attr('content') + '<br/>';
      var oldContent = $(this).parents('slide').children('div.footnotes').html();
      var newContent = oldContent + footnote;
      $(this).parents('slide').children('div.footnotes').html(newContent);
    });
  });
</script>


## SlateX

- What is it? 
- Why now?

## What is it?

- Tech Stack (updated: quarto and ghost)
- Quality Control  +  Payment Mechanisms
- Community

## Creator Economy

- Stripe
- "ultimately, as we think about the internet economy ...one of the big bets for us is on the creator economy" <footnote content=https://www.businessinsider.com/fintech-giant-stripe-is-betting-big-on-the-creator-economy-2021-5>
- a16z
- "There are thousands of experts, creators, and practitioners around the world who have valuable knowledge to share ... this is the best way for creators to monetize"<footnote content=https://www.protocol.com/maven-a16z-edtech-creator-economy">

## Creator Economy
- Point 72
- "[T]he creator economy...feels like it's turning into the new small business,...There are emerging employment trends going on..."<footnote content=https://www.businessinsider.com/point72-ventures-fintech-gig-creator-economies-social-media-influencer-2021-6>
- HBR "The Creator Economy Needs a Middle Class"
- "Subscription...can enable creators with even modest audience sizes to earn substantial amounts. These direct fan payment models facilitate greater monetization..."<footnote content=https://hbr.org/2020/12/the-creator-economy-needs-a-middle-class>

## Other Trends

- "No niche is too small if it's yours" - Seth Godin
- "Trust and influence now lie more with individuals than they do with institutions" -"Who can you trust?" Rachel Botsman
- Statista
- "It is projected that in 2027, 86.5 million people will be freelancing in the United States and will make up 50.9 percent of the total U.S. workforce." <footnote content = https://www.statista.com/statistics/921593/gig-economy-number-of-freelancers-us/>

## A few stories

- 25 hours of user feedback in June
- Here are a few snippets

## User Feedback 1

- silver dash: already turned down dollars for his Shiny app. Why? There is no way to monetize it (https://exploringfinance.shinyapps.io/goldsilver/). Retail getting more sophisticated. 
- the crypto and defi expert - and Shiny dev. This community wants to eliminate the middle man and trust the research. 
- GC the academic. Text books as dynamic documents with updating data would change the game.
- Two commodities traders and trainerpreneurs of aspiring traders: include zoom plugin and run dynamic content with live code. This is a super premium service - a real life project with two Pros. No other platform offers this. Direct lead in to quant recruiting *recurring theme
- The Canadian: dream is a webpage, where the user chooses reports and the data updates. He will charge $15k for this

## User Feedback 2

- R conf prof a platform whose time has come
- R conf hedgie the next evolution of data storytelling and a great resource for conferences
- The data and retail guru - next step in decentralized finance
-  make textbooks 100X better and 5X cheaper
- The backtester - built a backtest framework and tried to build a business, there was no community for paid work
- Open fin enthusiast research -> data -> code -> apps

## Recurrent Themes

- Reproducibility lends trust these days
- People are tired of trust me I'm from huge a company or a big university
- A better skills match freelance platform
- Quality is king
- Community compounds: attract creators, attract more readers

## Revenue Model

- For each creator, the platform keeps 20%
- We all grow together
- Each creator, with 1000 subscribers, \$10 per month ==  \$24k
- 3-Year Goal: 500 creators, avg'ing \$120k per year = \$10mm ARR
- 5-Year Goal: 1000 creators, avg'ing \$120k per year = \$25mm ARR
- 10-Year Goal: 4000 creators, avg'ing \$120k per year = \$96mm ARR

## Revenue Chart

```{r, echo = F}

tibble(
  creators    = c(10,       50,     500,        1000,         4000),
  subscribers = c(100,      500,     1000,       1000,         1000),
  time         = c("Alpha", "Beta", "Years 1-2", "Years 3-4", "Years 5-10"),
   revenue = creators * subscribers * 120 * .2
)  %>% 
  ggplot(aes(x = as.factor(creators), y = revenue, text = time)) +
  geom_col(fill = "steelblue", width = .5) +
  ggrepel::geom_label_repel(aes(label = time), nudge_y = 50, direction = "y") +
  scale_y_continuous(label = scales::dollar, breaks = scales::pretty_breaks(n = 10)) +
  labs(title = "Revenue Model For Subscription Only", x = "Creators", y = "") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = .5))
  
```

## Revenue Streams

- Research Subscriptions 
- Dynamic Textbooks
- Data vendor partnerships
- Conference papers
- Marketplace of models, data, and templates

## Back to the 3 pillars

- Tech
- Quality and Payment
- Community

## Tech Stack

- Rmarkdown, Shiny, Distill and Blastula -> Quarto
- Ghost as possible foundation with payment capability
- Subscriber manager via smtp, and split paid v. free

## Branding and Payment

- Things coders don't want to handle
- Just hard enough to discourage people

## Community

- RS has done huge things for R community. 
- This is the next evolution for that community
- It doesn't yet exist for Python - this is where slateX helps RS dominate that world too

## Thoughts on How this Fits for RStudio

- Revenue
- Uncorrelated with enterprise - a diversifier
- Win Python with Community

## Long Term Trends

- Coders will rule the ~~day~~ decade
- Population of R and Python coders growing fast
- Data ubiquitous
- Decentralization > Big Institutions
- Explosion in assets and quant fields
- Vincent, Vinovest, crypto, SPACs

## Features

- Ease of publishing
- Integrate with twitter and linkedin
- Flow to blog and website and email drips
- All on top of Rmarkdown
- RStudio Cloud, Rmd, Shinyapps.io, Distill - the pieces are there
- Need some elegant glue
- A payment and subscription layer


## Challenges

- Finding 1000 creators
- Consistency
- Long term thinking

