---
title: "SlateX"
subtitle: "A Subscription Platform for R and Python Creators"
author: "Jonathan Regenstein"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = NA, fig.height = 6)
options(htmltools.dir.version = FALSE)

library(tidyverse)
library(tidyquant)

```


# SlateX

+ What is it? 
+ Why now? 
+ Why us? 

---

# Long Term Trends

+ Coders will rule the ~~day~~ decade
+ Population of R and Python coders growing fast
+ Data ubiquitous
+ Decentralization > Big Institutions
+ Explosion in assets and quant fields

---

# Revenue: 3 Year Plan

+ 1000 creators * 1000 subscribers each * $10 per month == $24mm ARR

```{r, echo = F}


tibble(
  creators = c(10, 100, 500, 1000, 2000),
  subscribers = c(100, 200, 500, 1000, 1000),
  revenue = creators * subscribers * 10 * 12 * .2,
  time = c("Alpha", "Beta", "Years 1-2", "Year 3", "Years 4-5")
) %>% 
  ggplot(aes(x = as.factor(creators), y = revenue, text = time)) + 
  geom_col(fill = "steelblue", width = .5) +
  ggrepel::geom_label_repel(aes(label = time), nudge_y = 50, direction = "y") +
  scale_y_continuous(label = scales::dollar) +
  labs(title = "Revenue Model", x = "Creators", y = "") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = .5))
  
```

---

# Features

+ Ease of publishing
+ Integrate with twitter and linkedin
+ Flow to blog and website and email drips
+ All on top of Rmarkdown
+ How diff from Substack?

---

# Challenges

+ Finding 1000 creators
+ Consistency
+ Long term thinking

---

